Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-10-04 Latex_files/Thesis/chapters/chapter 5/main.tex
updates 04-10-2024

While \textit{mstm} does provide the amplitude matrix it is not
scaled to account for distance from the target to the detector.
We amend this by simply scaling according to the inverse square 
law. As the detector is moved further from the target the 
intensity distribution across the entire detector will decrease
substantially. Because of the fall off it is more computationally 7
efficient to instead consider only the central pixel of the 
detector rather than across the entire surface. If we consider 
the difference between the average intensity and the intensity 
of the central point we can see that after not even $20 \mu$ 
away from the target particle the average intensity across the 
surface is within $0.1\%$ of the central pixel. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{fall_off_with_distance.png}
	\caption{Normalised difference between the central pixel intensity
	$I(\theta, \phi)$ and the average pixel intensity over the surface
	of the optical fibre $\langle I \rangle$ as a function of distance.
	4 different optical detectors were tested (spherical coordinates 
	are given in the legend). While the choice of coordinates is 
	arbitrary they all demonstrate the same exponential decay.}
\end{figure}

@@

Evaluating how well Eq.~\eqref{eq:bayes} performs in predicting $\hat{\bf n}$
is difficult because we have discretised the orientation space meaning 
there will always be some degree of inaccuracy in our prediction. The Kullback-Liebler divergence method allows us to compare the divergence 
between two probability, namely Eq.~\eqref{eq:bayes} and a case scenario.
\begin{align}
	D_{KL}(P\parallel p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}), t)) = \sum P(t) \frac{P(t)}{p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}), t)} 
\end{align}

Where $P(t)$ is the case scenario we are comparing against. In an ideal
case our model would correctly predict the dimer's orientation with 
100\% accuracy:
\begin{align}
	\label{eq:best}
	p_{best} = P(t) =
	\begin{cases}
		1 & \text{when $\hat{\bf n}_\alpha$ = $\hat{\bf n}_{best}$}\\
		0 & \text{when $\hat{\bf n}_\alpha$ $\neq$ $\hat{\bf n}_{best}$}
	\end{cases}
\end{align}

In reality the distribution from Eq.~\eqref{eq:bayes} will assign some 
non-zero probability to every reference orientation. Therefore the 
divergence of Eq.~\eqref{eq:bayes} at each time step is given as:
\begin{align}
	D_{KL}(p_{best}\parallel p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}), t))
	= \ln \left[\frac{1}{p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}), t)}
	\right]
	\label{eq;kullback}
\end{align}

where a larger value of $D_{KL}$ indicates that our model is less confident 
in its prediction of the dimer's orientation. The divergence $D_{KL}$ thus 
illustrates the 'spread' in the estimated dimer orientation probability 
-- a distribution strongly peaked at some value would give us more 
confidence in that value than a near-uniform distribution where the 
scattering measurement could imply a wide range of possible orientations 
-- but it does not directly indicate our estimates actual accuracy. 
In order to reflect the accuracy of each prediction by using a weighting
function such as:
\begin{align}
	\omega_\alpha = \frac{1}{2} (\hat{\bf n}_{best} \cdot \hat{\bf n}_\alpha+1)
\end{align}

Which is just the normalised dot product between our estimate and the
best possible estimate, so for highly inaccurate estimations $D_{KL}$
is far greater than if we narrowly missed the $\hat{\bf n}_{best}$. With
this in mind the divergence for a single measurement is:

\begin{align}
	D_{KL}(p_{best}\parallel p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}), t))
	= \ln \left[\frac{1}{p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}), t)\omega_\alpha}
	\right]
\end{align}

Later we will show how we set a baseline for evaluating the performance 
of \eqref{eq:bayes} across an entire trajectory and how it handles common
errors in a static light scattering setup.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Brownian Simulation}
\label{sec:brownian}

We use the Brownian OT package developed by Fung~\textit{et~al} 
\cite{Vigilante2020} to simulate the motion of an asymmetric dimer (Figure~\ref{fig:dimer}a) within an optical trap. We simulate the 
motion of a dimer trapped in a highly focused Gaussian beam by 
calculating the optical forces imparted by the laser, and the 
Brownian force due to the surrounding fluid. MSTM provides the 
necessary T-matrix to compute the optical force via \textit{ott}. 
The Brownian force is found by computing the dimer's diffusion 
tensor according to the analytical solutions provided by Nir and 
Acrivos \cite{Nir1973}. We simulated a polystyrene dimer ($n = 
1.59$) in a suspension of water ($n_{med} = 1.33$) over the 
course of $1 \ s$ with a simulation time step of $1 \times 10^{-5} 
\ s$. We placed the dimer 4 microns below the trap focus at an 
angle $30^{\circ}$ from the horizontal, the resulting trajectory 
is shown below in Sec~\ref{sec:motion}. We chose these initial 
parameters because it demonstrates our model's performance in non 
steady state conditions.

The exact number of detectors was initially assumed to be arbitrary, in that it made no difference to our estimate whether we used 2 angles or 200. For practical purposes it seemed beneficial that we demonstrate our method works for a minimal number of detection angles, as geometric constraints come into play when trying to install a high number of detection fibres for any optical tweezer set up.

\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.49\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig4a.png}
	\end{subfigure}
	\begin{subfigure}{0.4\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig4b.png}
	\end{subfigure}
	\caption{Expected scattered signals from reference orientations -see fig~\ref{fig:dimer} - when: (a) all three detectors are in the X-Y plane, (b) when 1 detector is raised out of the X-Y plane.}
	\label{fig:detectors}
\end{figure}

When all of the detectors lie in the same plane the expected signal can appear identical despite the dimer being in completely different orientations. This is shown in Figure~\ref{fig:detectors} which plots the expected signals from 30 reference orientations, each point is labelled with its corresponding reference orientation, the fact that points have multiple labels is because the dimer's scattering is indistinguishable in these two reference orientation. It should be noted that these pairs are reflected in one or more axis which suggests that these are due to the arrangement of our detectors. More specifically, if the detectors are placed say in the x-y plane then only when the dimer is pointed nearly fully upright will the expected signal be entirely unique. This is illustrative of the difficulty behind the inverse light scattering problem; as one cannot always map a given signal to a particular parameter value.

To remedy this we raise the third detector out of the x-y plane; as such the expected signals from each reference orientation is unique. As seen between Figures \ref{fig:detectors}a \& b each reference orientation now has a unique scattering signal, though with only three detectors the difference in expected signals can appear insignificant. By adding a $4^{th}$ detector we can differentiate signals more reliably, improving the neural networks performance.   In line with our goal of making this method viable in a laboratory setting we decided not to increase the number of detectors further than 4.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testing the Model}
\label{sec:test}
Using our simulation from Section~\ref{sec:brownian} we simulated the motion of a silica dimer ($n = 1.45$) trapped in water ($n = 1.33$) within a 5 mW optical trap. The trapping laser is 1064nm NIR focused through a 1.25 NA objective. The dimer is comprised of two tangent spheres with radii $1 \mu m$ and $0.5 \mu m$ respectively. We simulated the first 10 seconds of motion, calculating the orientation and position every 1 ms.

We applied Eq.~\eqref{eq:bayes}, taking the reference orientation with the highest probability  as our estimate of the dimer's instantaneous orientation $\hat{\bf n}_{est}$. To visualise the model's performance  we plotted the radial distance between our estimation $\hat{\bf n}_{est}$ and the dimer's \emph{actual} instantaneous orientation $\hat{\bf s}$ versus time. For comparison, we also plotted the radian distance between the  dimer's instantaneous orientation and the closest reference orientation, denoted $\hat{\bf n}_{best}$. The dotted line indicates the maximum radian distance ($0.896$ radians) between two \textit{neighbouring} reference orientations: if we are under this line then we know our estimate is at least neighbouring the best result. Assuming a uniform prior of the reference orientations $p(\hat{\bf n}_\alpha)$  the neural network's predictions ($\hat{\bf n}_{est}$ from Eq.~\eqref{eq:bayes}) are at times reasonable, but there are significant large and random jumps away from the correct result (Fig.~\ref{fig:uniform}).

\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{fig5.png}
	\caption{Model's estimation of dimer orientation over the simulation time, assuming uniform prior $p(\hat{\bf n}_\alpha)$, broken up into x, y, and z components for clarity. Blue line denotes the best result we can achieve (the reference orientation $\hat{\bf n}_{best}$ that is closest to the actual orientation), orange line denotes the result provided by eq~\ref{eq:bayes}: where the orange line is not visible, the model's prediction agrees with $\hat{\bf n}_{best}$. Dotted black line is the instantaneous orientation $\hat{\bf s}$.}
	\label{fig:uniform}
\end{figure}

One reason we observe such large jumps in the estimated 
orientation is simply because the neural network is assuming
that the signals are unrelated from one another. As demonstrated
by fig~\ref{fig:mixing} the orientation and signal spaces are 
uncorrelated with one another which results in the neural network
to assign orientations incorrectly. Combining this fact with 
use of a uniform prior ($p(\hat{\bf n}_\alpha)$), there 
is no constraint on how much estimated orientation can change 
from time-step to time-step.

@@

As shown in Figure~\ref{fig:biased} implementation of Eq~\eqref{eq:boltz} helps significantly reduce the large random excursions of estimated orientation away from the 'best' result.

\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{fig8a.png}
	\caption{\label{fig:biased}
		%
		Estimation of dimer orientation with $p(\hat{\bf n}_\alpha)$ defined
		by Eq~\eqref{eq:boltz}.  Blue line denotes the best result we can
		achieve, orange line denotes the result provided by eq~\ref{eq:bayes}.
		Dotted black line is the instantaneous orientation $\hat{\bf s}$ (see Section~\ref{sec:Bayes}).
		%
	}
\end{figure}

The simulation data from Section~\ref{sec:brownian} was used to evaluate our model's performance --- covered in Section~\ref{sec:divergence}. By summing the divergence of each measurement across the entire simulation we get an evaluation of how well the model performed in estimating the dimer's orientation. To compare the effects of changing certain parameters on the performance of our model we compare our result of $K_{l,total}$ to a worst case scenario and evaluate how much it improves upon this, denoted as $F(K_l)$:
\begin{align}
	K_{l, \ total} &= \sum\limits_{\# =1}^{timesteps} K_{l,\#}
	\\
	K_{l, \ worst} &= \sum\limits_{\#=1}^{timesteps} \ln \left[\frac{1}{1/n_{ref}} \right]
	\\
	F(K_l) &= \frac{K_{l,\ worst}}{K_{l, \ total}}
\end{align}

The worst case scenario is akin to randomly choosing a reference
orientation at each time step. The greater the value of $F(K_l)$, the
better our model's confidence is in characterising the dimer's
motion. Because our model is dependent on several parameters we need
to a sophisticated method for understanding how these parameters
correlate with $F(K_l)$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymmetric dimer dynamics}
\label{sec:motion}
A simulation of a asymmetric dimer ($a_1=1\,\mu{\rm m}$, $a_2=0.5\,\mu{\rm m}$) 
trapped in an off-axis trapping orientation was used as a test case for our 
model, since it was previously shown that dimers can be optically rotated

\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{fig7a.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig7b.png}
	\end{subfigure}
	\caption{Simulation results of: (a) the dimer's orientation vector with time, (b) the dimer's [x,y,z] position with time.}
	\label{fig:motion}
\end{figure}

In the simulations of Vigilante~\emph{et~al}.\ \cite{Vigilante2020}, trapped symmetrical dimers were investigated; their findings showed that the optical torque on the dimer goes to zero while aligned vertically and is at its maximum in a horizontal alignment. However as seen in Figure~\ref{fig:motion} asymmetric dimers demonstrate dynamics that do not immediately achieve steady state. We chose to use asymmetric dimers as our benchmark due to this fact, as its orientational motion is far more complex than a symmetric dimer. In the future we hope to further investigate the motion of asymmetric dimers. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Accounting for sources of error in light scattering measurements}
When it comes to analysing light scattering from any size particle, error analysis becomes a significant factor. Typically this can be accounted for by averaging over long periods of time to get an assessment of the steady state conditions of the target particle. However in our case where we wish to know the instantaneous orientation, we instead have to rely on our understanding of how uncertainty can effect our model's performance. We identified two areas which are likely sources of error in our estimation: firstly, an incorrect modelling of the target particle, and secondly, signal noise arising from experimental factors. We highlight how we address these areas below. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subparagraph{Impact of incorrect dimer sizing}
\label{sec:lam}

One of the main limitations of our model is that we assume that the dimer being modelled in MSTM is accurate to the dimer being trapped in the optical tweezer. Sizing molecules accurately is a significant challenge for single particle analysis so there is bound to be some uncertainty with the measurements. We ran our model 3 times with the neural net being trained on a dimer of size ratio $1:1.95$, $1:2.00$ and $1:2.05$.
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.33\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{fig8a.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig8b.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig8c.png}
	\end{subfigure}
	\caption{Model estimates of orientation when neural net has been trained on dimer of size ratio: (a) 1:2 $[F(K_l)=9.456]$, (b) 1:2.05 $[F(K_l)=1.324]$, (c) 1:1.95 $[F(K_l)=1.325]$ ($n_{refs} = 30$)}
	\label{fig:size}
\end{figure}

As can be seen from Fig~\ref{fig:size}  even the slightest change in size ratio makes a very significant difference to the performance of our model. This amounts to just over $100 \ nm$ in the dimer's overall size, yet results in our model being correct from over 90 \% of the time to now as low as 30 \%. This highlights the importance of correctly sizing trapped entities before performing any in depth analysis of the scattering pattern, as even the slightest deviation can have a serious impact. We addressed this by increasing the number of available reference orientations from 30 to 126 (following the same procedure as given by \cite{Reyuthor2006} to evenly space out the coordinates) and increasing the weighting factor in Eq~\ref{eq:boltz}. While this didn't have a significant improvement on the overall accuracy of the model, in the worst case having a slight increase from 30.5 \% to 40.3 \%, it did help to significantly reduce the magnitude between our model's estimations and the dimer's motion as seen below in Fig~\ref{fig:refs}.
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{fig9a.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig9b.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig9c.png}
	\end{subfigure}
	\caption{Model estimates of orientation when neural net has been trained on dimer of size ratio: (a) 1:2 $[F(K_l)=11.756]$, (b) 1:2.05 $[F(K_l)=1.233]$, (c) 1:1.95 $[F(K_l)=2.128]$, ($n_{refs} = 126$)}
	\label{fig:refs}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig10a.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig10b.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig10c.png}
	\end{subfigure}
	\caption{Model prediction for signal error of (a) $1\%$ ~  $[F(K_l)=7.246]$, (b) $15\%$ $[F(K_l)=0.511]$, and (c) $25\%$ ~  $[F(K_l)=0.536]$.}
	\label{fig:epsilon}
\end{figure}

As can be seen from Figure~\ref{fig:epsilon}, the inclusion of signal noise quickly leads to a decrease in the model's performance. This is due to an inherent feature of the inverse scattering problem: two distinct regions in orientation space can become heavily intertwined and thus no longer well separated when mapped to intensity space (even though the mapping remains continuous): so even small uncertainties in the scattering data can lead to large 'mistakes' in the choice of orientation by the neural network. (Indeed if this was not the case the inverse scattering problem would be quite simple.)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{QPD Simulations}
A QPD is simply a measure of the total electric field incident on a photo diode, in order to accurately simulate a QPD response careful consideration of how the Electromagnetic fields are defined is required.

>>>>

While \textit{mstm} does provide the amplitude matrix it is not
scaled to account for distance from the target to the detector.
We amend this by simply scaling according to the inverse square 
law. As the detector is moved further from the target the 
intensity distribution across the entire detector will decrease
substantially. Because of the fall off it is more computationally 7
efficient to instead consider only the central pixel of the 
detector rather than across the entire surface. If we consider 
the difference between the average intensity and the intensity 
of the central point we can see that after not even $20 \mu$ 
away from the target particle the average intensity across the 
surface is within $0.1\%$ of the central pixel. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{fall_off_with_distance.png}
	\caption{Normalised difference between the central pixel intensity
	$I(\theta, \phi)$ and the average pixel intensity over the surface
	of the optical fibre $\langle I \rangle$ as a function of distance.
	4 different optical detectors were tested (spherical coordinates 
	are given in the legend). While the choice of coordinates is 
	arbitrary they all demonstrate the same exponential decay. Dashed
	lines indicate the difference after $20\mu m$ from the trap focus,
	in most practical cases getting an optical fibre any closer would
	disrupt the trap stability.}
\end{figure}

@@

Evaluating how well Eq.~\eqref{eq:bayes} performs in predicting $\hat{\bf n}$
is difficult because we have discretised the orientation space meaning 
there will always be some degree of inaccuracy in our prediction. The Kullback-Liebler divergence method provides a measure of the relative
entropy change between two probability distributions:
\begin{align}
	D_{KL}(P(t)\parallel Q(t)) = \sum P(t) \log_2\left[\frac{P(t)}{Q(t)}\right] 
	\label{eq:D_KL}
\end{align}

Where $P(t)$ and $Q(t)$ are two probability distributions we are
comparing, often it is common to use a base 2 log as this converts 
the entropy to base 2. By relative entropy we are talking about 
the useful information gained/lost by switching from $P(t)$ to 
$Q(t)$. In our case $Q(t)$ is simply the distribution given by
Eq.~\eqref{eq:bayes} and $P(t)$ is an idealised distribution, 
one where the model is accurate with 100\% certainty.
\begin{align}
	\label{eq:best}
	p_{best} = P(t) =
	\begin{cases}
		1 & \text{when $\hat{\bf n}_\alpha$ = $\hat{\bf n}_{best}$}\\
		0 & \text{when $\hat{\bf n}_\alpha$ $\neq$ $\hat{\bf n}_{best}$}
	\end{cases}
\end{align}

In reality the distribution from Eq.~\eqref{eq:bayes} will assign 
some non-zero probability to every reference orientation. Therefore 
the relative entropy for a single measurement is given as:
\begin{align}
	D_{KL}(p_{best}\parallel p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}), t))
	= \log_2 \left[\frac{1}{p(\hat{\bf n}_\alpha| y_k(\hat{\bf s}), t)}
	\right]
	\label{eq:kullback}
\end{align}

The relative entropy is a measure if how spread out our distribution
is. With larger values of $D_{KL}$ indicating that our prediction is 
spread out so the correct orientation is unsure about $\hat{\bf n}_
{best}$. Whereas a low value of $D_{KL}$ means that our model is more 
confident in $\hat{\bf n}_{best}$. The only draw back being that the 
relative entropy does nothing to indicate accuracy, only how closely 
our distribution matches our ideal result. This will be better 
exemplified later in \ref{sec:test}.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Brownian Simulation}
\label{sec:brownian}

We use the Brownian OT package developed by Fung~\textit{et~al} 
\cite{Vigilante2020} to simulate the motion of an asymmetric dimer (Figure~\ref{fig:dimer}a) within an optical trap. We simulate the 
motion of a dimer trapped in a highly focused Gaussian beam by 
calculating the optical forces imparted by the laser, and the 
Brownian force due to the surrounding fluid. We simulated a 
polystyrene dimer ($n = 1.59$) in a suspension of water ($n_{med} 
= 1.33$). As discussed in chapter 4 dimers can be stably trapped
in off-axis orientations. We simulate a dimer (of size ratio 2) that
is trapped in this off-axis orientation by a $5 mW$ laser, due to 
the meta-stability of the trap the dimer is only trapped for second
before it escapes the trap. The dimer's position and orientation 
is shown below:
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{fig7a.png}
	\end{subfigure}
	\begin{subfigure}{0.45\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig7b.png}
	\end{subfigure}
	\caption{Simulation results of: (a) the dimer's orientation vector with time, (b) the dimer's [x,y,z] position with time.}
	\label{fig:motion}
\end{figure}

At the same we use \textit{mstm} to replicate the intensity of light
incident on the surfaces of detectors placed around the focus of the
optical trap. The exact number of detectors was initially assumed to 
be arbitrary, in that it made no difference to our estimate whether 
we used 2 angles or 200. For practical purposes it seemed beneficial 
that we demonstrate our method works for a minimal number of detection 
angles, as geometric constraints come into play when trying to install 
a high number of detection fibres for any optical tweezer set up.

When all of the detectors lie in the same plane the expected signal 
can appear identical despite the dimer being in completely different orientations. It should be noted that these pairs are reflected in 
one or more axis which suggests that these are due to the arrangement 
of our detectors. More specifically, if the detectors are placed say 
in the x-y plane then only when the dimer is pointed nearly fully 
upright will the expected signal be entirely unique. This is not an 
issue with typical analytical static light scattering experiments 
because the signal being collected is averaged over a population of 
particles all in different orientations. Whereas in our set up we are concerned with the scattering of a single particle whose scattering is orientationally dependant.

To remedy this we raise the third detector out of the x-y plane; 
as such the expected signals from each reference orientation is 
unique, though with limited resolution. By adding a $4^{th}$ 
detector we can differentiate signals more reliably, improving the 
neural networks performance. In line with our goal of making this 
method viable in a laboratory setting we decided not to increase 
the number of detectors further than 4.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Testing the Neural Network}
\label{sec:test}
We applied Eq.~\eqref{eq:bayes}, taking the reference orientation 
with the highest probability  as our estimate of the dimer's 
instantaneous orientation $\hat{\bf n}_{est}$. To visualise the 
model's performance we plotted the orientation components of our 
estimation $\hat{\bf n}_{\alpha}$ and the dimer's \emph{actual} 
instantaneous orientation $\hat{\bf s}$ versus time. For comparison, 
we also plotted the orientation components of the closest reference orientation, $\hat{\bf n}_{best}$. Assuming a uniform prior of the 
reference orientations $p(\hat{\bf n}_\alpha)$ the neural network's predictions ($\hat{\bf n}_{\alpha}$ from Eq.~\eqref{eq:bayes}) are 
at times reasonable, but there are significant large and random jumps 
away from the correct result (Fig.~\ref{fig:uniform}). 
\begin{figure}[h!]
	\centering
	\includegraphics[width=\textwidth]{fig5.png}
	\caption{Model's estimation of dimer orientation over the simulation time, assuming uniform prior $p(\hat{\bf n}_\alpha)$, broken up into x, y, and z components for clarity. Blue line denotes the best result we can achieve (the reference orientation $\hat{\bf n}_{best}$ that is closest to the actual orientation), orange line denotes the result provided by eq~\ref{eq:bayes}: where the blue line is not visible, the model's prediction agrees with $\hat{\bf n}_{best}$. Dotted black line is the instantaneous orientation $\hat{\bf s}$.}
	\label{fig:uniform}
\end{figure}

One reason we observe such large jumps in the estimated 
orientation is simply because the neural network is assuming
that the signals are unrelated from one another. We can 
observe this if we take the average relative entropy change
across the entire trajectory:

\begin{align}
	\langle D_{KL}\rangle = \frac{1}{N} \sum_{i=1}^{N} \log_2 \left[\frac{1}{p(\hat{\bf n}_\alpha\parallel y_k(\hat{s}),t_i)}\right]
	\label{eq:score}
\end{align}

Where we get an average entropy change of $\approx 0.604$, in 
base 2 this means that on average the model has narrowed down 
its options from 1 in 30 to 1 in 1.52. This is not reflected
though in fig.~\ref{fig:uniform} which indicates that while 
the model is highly confident in its results it is not at all 
accurate. As demonstrated by fig~\ref{fig:mixing} the 
orientation and signal spaces are uncorrelated with one another 
which results in the neural network to assign orientations 
incorrectly. Combining this fact with use of a uniform prior 
($p(\hat{\bf n}_\alpha)$), there is no constraint on how much 
estimated orientation can change from time-step to time-step.

@@

As shown in Figure~\ref{fig:biased} implementation of Eq~\eqref{eq:boltz} helps significantly reduce the large random excursions of estimated orientation away from the 'best' result. However at the same 
time result is still subpar.
\begin{figure}[h]
	\centering
	\includegraphics[width=\textwidth]{fig8a.png}
	\caption{\label{fig:biased}
		%
		Estimation of dimer orientation with $p(\hat{\bf n}_\alpha)$ defined
		by Eq~\eqref{eq:boltz}.  Blue line denotes the best result we can
		achieve, orange line denotes the result provided by eq~\ref{eq:bayes}.
		Dotted black line is the instantaneous orientation $\hat{\bf s}$ (see Section~\ref{sec:Bayes}).
		%
	}
\end{figure}

Once again using Eq.~\eqref{eq:score} we now get a result of 
$\approx 0.204$ or a 1 in 1.2 result. This is only a slight 
improvement in terms of confidence but has drastically reduced 
the variation in our models predictions. There are other 
improvements that can be made, which additionally also help with
potential sources of error in our set up.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Accounting for sources of error in light scattering measurements}
When it comes to analysing light scattering from any size particle,
error analysis becomes a significant factor. Typically this can be 
accounted for by averaging over long periods of time to get an 
assessment of the steady state conditions of the target particle. 
However in our case where we wish to know the instantaneous 
orientation, we instead have to rely on our understanding of how 
uncertainty can effect our model's performance. We identified two 
areas which are likely sources of error in our estimation: firstly, 
an incorrect modelling of the target particle, and secondly, signal 
noise arising from experimental factors. We highlight how we address 
these areas below. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subparagraph{Impact of incorrect dimer sizing}
\label{sec:lam}

One of the main limitations of our model is that we assume that 
the dimer being modelled in \textit{mstm} is accurate to the 
dimer being trapped in the optical tweezer. Sizing molecules 
accurately is a significant challenge for single particle 
analysis so there is bound to be some uncertainty with the 
measurements. We ran our model 3 times with the neural net being 
trained on a dimer of size ratio $1:1.95$, $1:2.00$ and $1:2.05$.
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.33\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{fig8a.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig8b.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig8c.png}
	\end{subfigure}
	\caption{Model estimates of orientation when neural net has 
		been trained on dimer of size ratio: (a) 1:2 $[\langle D_{KL}\rangle=0.519]$, (b) 1:2.05 $[\langle D_{KL}
		\rangle=3.706]$, (c) 1:1.95 $[\langle D_{KL}\rangle=
		3.705]$ ($n_{refs} = 30$)}
	\label{fig:size}
\end{figure}

As can be seen from Fig~\ref{fig:size}  even the slightest change in size ratio makes a very significant difference to the performance of our model. This amounts to just over $100 \ nm$ in the dimer's overall size, yet results in our model being correct from over 90 \% of the time to now as low as 30 \%. This highlights the importance of correctly sizing trapped entities before performing any in depth analysis of the scattering pattern, as even the slightest deviation can have a serious impact. We addressed this by increasing the number of available reference orientations from 30 to 126 (following the same procedure as given by \cite{Reyuthor2006} to evenly space out the coordinates) and increasing the weighting factor in Eq~\ref{eq:boltz}. While this didn't have a significant improvement on the overall accuracy of the model, in the worst case having a slight increase from 30.5 \% to 40.3 \%, it did help to significantly reduce the magnitude between our model's estimations and the dimer's motion as seen below in Fig~\ref{fig:refs}.
\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width =\textwidth]{fig9a.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig9b.png}
	\end{subfigure}
	\begin{subfigure}{0.31\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig9c.png}
	\end{subfigure}
	\caption{Model estimates of orientation when neural net has 
		been trained on dimer of size ratio: (a) 1:2 $[\langle D_{KL}\rangle=0.593]$, (b) 1:2.05 $[\langle D_{KL}\rangle
		=5.659]$, (c) 1:1.95 $[\langle D_{KL}\rangle=3.279]$, 
		($n_{refs} = 126$)}
	\label{fig:refs}
\end{figure}

@@

\begin{figure}[h!]
	\centering
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig10a.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig10b.png}
	\end{subfigure}
	\begin{subfigure}{0.32\textwidth}
		\subcaption{}
		\includegraphics[width=\textwidth]{fig10c.png}
	\end{subfigure}
	\caption{Model prediction for signal error of (a) $1\%$ ~
		$[\langle D_{KL}\rangle=0.962]$, (b) $15\%$ $[\langle D_{KL}\rangle=13.654]$, and (c) $25\%$ ~  $[\langle D_{KL}\rangle=13.017]$.}
	\label{fig:epsilon}
\end{figure}

As can be seen from Figure~\ref{fig:epsilon}, the inclusion of 
signal noise quickly leads to a decrease in the model's 
performance. So much so that beyond 15\% the model is actually 
worse than just randomly guessing.This is due to an inherent 
feature of the inverse scattering problem: two distinct regions 
in orientation space can become heavily intertwined and thus no 
longer well separated when mapped to intensity space (even 
though the mapping remains continuous): so even small 
uncertainties in the scattering data can lead to large 'mistakes' 
in the choice of orientation by the neural network. (Indeed if 
this was not the case the inverse scattering problem would be 
quite simple.)

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{QPD Simulations}
A QPD is simply a measure of the total electric field incident on a photo diode, in order to accurately simulate a QPD response careful consideration of how the Electromagnetic fields are defined is required.
